---
title: "608_Final_Project"
author: "Jose Mawyin"
date: "5/9/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=6)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
library(readr)
library(dplyr)
library(ggplot2)
library(forecast) #To Analyze TimeSeries
library(tictoc) #Timing Processes
library(stringr)
library(tidyr)
library(maditr) #Data Aggregation
library(lubridate)
library(plyr)
library(viridis) # colour blind friendly palette, works in B&W also
library(ggeffects) #Create Tidy Data Frames of Marginal Effects for 'ggplot' from Model Outputs
library(ggiraphExtra) #Make Interactive 'ggplot2'
library(nnet)
library(ROCR)
library(car)
load("more/nc.RData")
```

## R Markdown

```{r}
London.Energy.2013<- read_csv("/Users/josemawyin/607_Final_Project/London.Energy.2013.csv")
glimpse(London.Energy.2013)
```
```{r}
table(London.Energy.2013$Acorn)
```
```{r}
table(London.Energy.2013$Acorn_grouped)
```


```{r,eval=FALSE}
#**Subsetting by type of Acorn_grouped:**
London.Energy.2013.Comfortable <- filter(London.Energy.2013, str_detect(London.Energy.2013$Acorn_grouped, 'Comfortable'))
write.csv(London.Energy.2013.Comfortable, "/Users/josemawyin/607_Final_Project/London.Energy_2013_Comfortable.csv")
#rm(London.Energy.2013)
#**Subsetting by type of meter:**
London.Energy.2013.Comfortable.Std <- filter(London.Energy.2013.Comfortable, str_detect(London.Energy.2013.Comfortable$stdorToU, 'Std'))
write.csv(London.Energy.2013.Comfortable.Std, "/Users/josemawyin/607_Final_Project/London.Energy_2013_Comfortable_Std.csv")
London.Energy.2013.Comfortable.ToU <- filter(London.Energy.2013.Comfortable, str_detect(London.Energy.2013.Comfortable$stdorToU, 'ToU'))
write.csv(London.Energy.2013.Comfortable.ToU, "/Users/josemawyin/607_Final_Project/London.Energy_2013_Comfortable_ToU.csv")
rm(London.Energy.2013.Comfortable)
```

*London.Energy_2013_Comfortable_Std.csv
*London.Energy_2013_Comfortable_ToU.csv

*London.Energy_2013_Affluent_Std.csv
*London.Energy_2013_Affluent_ToU.csv

*London.Energy_2013_Adversity_Std.csv
London.Energy_2013_Adversity_ToU.csv


```{r, eval=FALSE}
London.Energy.2013.L.ToU<- read_csv("/Users/josemawyin/607_Final_Project/London.Energy_2013_Adversity_ToU.csv")
Number.Houses <- aggregate(X1 ~ LCLid, London.Energy.2013.L.ToU, function(x) length(unique(x)))
attach(London.Energy.2013.L.ToU)
Number.Houses <- aggregate(X1 ~ LCLid, London.Energy.2013.L.ToU, function(x) length(unique(x)))
Full.Year <- filter(Number.Houses, str_detect(Number.Houses$X1, '17532'))

Full.Year.Data <- filter(London.Energy.2013.L.ToU, London.Energy.2013.L.ToU$LCLid %in% Full.Year$LCLid)
Full.Year.Data <- select(Full.Year.Data, DateTime, LCLid, KWH.hh..per.half.hour.)
Full.Year.Data$DateTime <- as.factor(Full.Year.Data$DateTime)
Full.Year.Data$KWH.hh..per.half.hour. <-as.integer(1000*Full.Year.Data$KWH.hh..per.half.hour. ) 
glimpse(Full.Year.Data)
Houses <- 420768/17532

Wide.2013.L.ToU <- dcast(Full.Year.Data, DateTime ~ Full.Year.Data$LCLid, value.var = "KWH.hh..per.half.hour.", fun.aggregate = sum)
Wide.2013.L.ToU.size <- dim(Wide.2013.L.ToU)

average.2013.L.ToU <- data.frame(ID=Wide.2013.L.ToU[,1], Means=rowMeans(Wide.2013.L.ToU[,-1]))
#head(average.2013.L.ToU)

attach(average.2013.L.ToU)
average.2013.L.ToU$DateTime <- as_datetime(average.2013.L.ToU$DateTime)
average.2013.L.ToU$ymd <-ymd_hms(DateTime)
average.2013.L.ToU$month <- month(average.2013.L.ToU$ymd, label = TRUE)
average.2013.L.ToU$year <- year(average.2013.L.ToU$ymd)
average.2013.L.ToU$wday <- wday(average.2013.L.ToU$ymd, label = TRUE)
average.2013.L.ToU$hour <- hour(average.2013.L.ToU$ymd)
attach(average.2013.L.ToU)
#head(average.2013.L.ToU)
#write.csv(average.2013.L.ToU, "/Users/josemawyin/607_Final_Project/Ave_London.Energy_2013_Adversity_ToU.csv")

dayHour <- ddply(average.2013.L.ToU, c( "hour", "wday"), summarise,
                    N    = mean(Means)
)

#reverse order of months for easier graphing
dayHour$wday <- factor(dayHour$wday, levels=rev(levels(dayHour$wday)))
dayHour$Acorn_group <- as.factor("Adversity")
dayHour$stdorToU <- as.factor("Std")
#write.csv(dayHour, "/Users/josemawyin/607_Final_Project/dayHour.csv")
head(dayHour)
attach(dayHour)
```

```{r}
United_dayHour<-rbind(United_dayHour, dayHour)
table(United_dayHour$stdorToU, United_dayHour$Acorn_group)
#write.csv(United_dayHour, "/Users/josemawyin/607_Final_Project/United_dayHour.csv")
```

```{r, warning=FALSE, echo=FALSE, message=FALSE}
average_group <- read.csv("/Users/josemawyin/607_Final_Project/Ave_London.Energy_2013_Adversity_ToU.csv")
e <- ggplot(average_group, aes(y= Means, x = ymd))
e +  geom_point(size = 0.1) + geom_smooth(method = 'auto') +
  theme_bw() + theme_minimal() +
  labs(title = "Annual Seasonality in Electricity Comsumtion ",
       x = "Date", y = "Electricity Comsumtion (watt.hours.hour)") 
```

*London.Energy_2013_Comfortable_Std.csv
*London.Energy_2013_Comfortable_ToU.csv

*London.Energy_2013_Affluent_Std.csv
*London.Energy_2013_Affluent_ToU.csv

London.Energy_2013_Adversity_Std.csv
London.Energy_2013_Adversity_ToU.csv
```{r}
tariff_data <- read_csv("/Users/josemawyin/607_Final_Project/tariff_data.csv")
average.2013.L.ToU <- read_csv("/Users/josemawyin/607_Final_Project/Ave_London.Energy_2013_Adversity_ToU.csv")
average.2013.L.Std <- read_csv("/Users/josemawyin/607_Final_Project/Ave_London.Energy_2013_Adversity_Std.csv")

L.ToU.and.Std <- data.frame(data.frame(matrix(NA, nrow = 17520, ncol = 1)))
attach(L.ToU.and.Std)
L.ToU.and.Std$DateTime <- average.2013.L.ToU$DateTime
L.ToU.and.Std$Tariff_Factor <- tariff_data$Tariff_factor
L.ToU.and.Std$Tariff_Number <- tariff_data$Tariff
L.ToU.and.Std$L.ToU.Average <- average.2013.L.ToU$Means
L.ToU.and.Std$L.Std.Average <- average.2013.L.Std$Means
L.ToU.and.Std$Difference <- average.2013.L.ToU$Means - average.2013.L.Std$Means
L.ToU.and.Std$Tariff_Factor <- factor(L.ToU.and.Std$Tariff_Factor, levels = c("High", "Normal", "Low")) #Reorder Factors
#Separating Date and Time
#L.ToU.and.Std$DateTime <- as_datetime(L.ToU.and.Std$DateTime)
L.ToU.and.Std$ymd <-ymd_hms(average.2013.L.ToU$DateTime)
L.ToU.and.Std$month <- month(L.ToU.and.Std$ymd, label = TRUE)
L.ToU.and.Std$year <- year(L.ToU.and.Std$ymd)
L.ToU.and.Std$wday <- wday(L.ToU.and.Std$ymd, label = TRUE)
L.ToU.and.Std$hour <- hour(L.ToU.and.Std$ymd)
L.ToU.and.Std$hour < as.factor(L.ToU.and.Std$hour)
L.ToU.and.Std <- L.ToU.and.Std[-1]
write.csv(L.ToU.and.Std, "/Users/josemawyin/607_Final_Project/Adversity.ToU.and.Std.csv")
```

```{r, warning=FALSE, echo=FALSE}
boxplot_data <- read_csv("/Users/josemawyin/607_Final_Project/Adversity.ToU.and.Std.csv")
d <- ggplot(boxplot_data, aes(x = Tariff_Factor, y = Difference, color=Tariff_Factor))
d + geom_point(aes(shape=Tariff_Factor),size=0.3) + geom_jitter(aes(shape=Tariff_Factor),size=0.3,height = 0.5, width = 0.5) + geom_boxplot(outlier.shape=16, aes(group=Tariff_Factor), alpha = 0.3,
             outlier.size=1, notch=TRUE) +
  stat_summary(geom = "point", fun.y = "mean", col = "black", size = 3, shape = 24, fill = "red") + labs(title = "Boxplot and Jittered Histogram of Electricity Demand Vs Pricing Signal \nDifference Mean Shown by Red Triangle",
       x = "Electricity Pricing Signal", y = "Difference in Electricity Demand [ToU - STd] (kw.hh.h)") + coord_flip()
```

```{r}
Comfortable <- read_csv("/Users/josemawyin/607_Final_Project/Comfortable.ToU.and.Std.csv")
Affluent <- read_csv("/Users/josemawyin/607_Final_Project/Affluent.ToU.and.Std.csv")
Adversity <- read_csv("/Users/josemawyin/607_Final_Project/Adversity.ToU.and.Std.csv")
```

```{r}
Adversity$Acorn_Group <- "Adversity"
Affluent$Acorn_Group <- "Affluent"
Comfortable$Acorn_Group <- "Comfortable"
```

```{r}
Joint_Acorn_Group <- rbind(Adversity,Affluent,Comfortable)
write.csv(Joint_Acorn_Group, "/Users/josemawyin/607_Final_Project/Joint_Acorn_Group.csv")
table(Joint_Acorn_Group$Acorn_Group)
```

```{r}
head(Joint_Acorn_Group)
table(Joint_Acorn_Group$Tariff_Factor)
```

